Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Use assertEqual instead of @=?

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
spec :: Spec
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      reverse [1 :: Int, 2, 3] @?= [3, 2, 1]

@@

The problem of the original Hspec is that it does not provide
a mechanism to express \emph{expectation}\/s with
BDD terminology.
For instance,
it still uses HUnit
assertions (e.g. \verb|@?=| in the example above), which are TDD
terminologies. In BDD, they are replaced with design terminologies.
The following Rspec example shows the ``should'' expectation keyword:

>>>>

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
spec :: Spec
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      assertEqual "" [3, 2, 1]
                     (reverse [1 :: Int, 2, 3])

@@

The problem of the original Hspec is that it does not provide
a mechanism to express \emph{expectation}\/s with
BDD terminology.
For instance,
it still uses HUnit
assertions, which are TDD
terminologies. In BDD, they are replaced with design terminologies.
The following Rspec example shows the ``should'' expectation keyword:
